Generality in food webs scales with species richness, not latitude

### 2015-03-23 manuscript/latitudepaper.tex
Updated results for by_TL models

We compiled a list of 263 empirical food webs from
multiple sources (see Supplemental Information for web origins and selection
criteria). We recorded study site latitude from the original source where
possible or, where study sites were described but exact coordinates were not
given, obtained estimated coordinates using Google Earth \citep{GoogleEarth}.

@@

For relationships of $Z$, $G$, and $V$ to $S$, equation~\ref{LogLog} had a lower AIC than the corresponding
equation~\ref{Power}. This indicates that the data support an assumption of multiplicative log-normal
error better than an assumption of additive normal error. That is, [[but what does it mean?]] . 
We therefore used logarithmic-form models when assessing the effect of latitude on scaling relationships 
with $S$.

Contrary to the expected latitudinal gradient, the best-fit version of equation~\ref{Latfull} for $S$
did not include a term for latitude or any of its interactions with ecosystem type. Species richness was
higher for stream ecosystems ($\alpha_{2:Stream}$=22.4, $p$\textless0.001) than other ecosystem types. 
Similarly, the best-fit version of equation~\ref{Latfull} for $G$ did not include 
any terms for latitude or interactions between latitude and ecosystem type. $G$ was lower in terrestrial
and lake food webs than in other ecosystem types ($\alpha_{2:Terrestrial}$=-3.77, $p$\textless0.001 and 
$\alpha_{2:Lake}$=-1.98, $p$=0.044). The best-fit models for $Z$ and $V$ did not include any terms for
latitude, ecosystem type, or their interactions.
the best-fit version of equation~\ref{Latfull} for $Z$ did not include a term for latitude,
ecosystem type, or any of their interactions. Food webs tended to contain about 3.53 links per species
($p$\textless0.001), with the average species being preyed upon by 3.53 predators ($p$\textless0.001).

\subsection*{Effect of Latitude on Scaling with S}

The effect of latitude on scaling relationships varied across ecosystem types.
Overall, specialization in marine and terrestrial food webs increased towards the poles, 
while specialization in lake food webs increased towards the equator (Fig.~\ref{scalinfig}). 
In estuarine and stream food webs, there was a great deal of variation, with links per species
and vulnerability increasing towards the poles and generality increasing towards the equator.
More specifically, the scaling of mean links per species with species richness increased with
increasing latitude ($\beta_{Latitude}$=0.004, $p$\textless0.001; Table~\ref{Bestfits}). This
increase, however, was reversed for marine and terrestrial food webs
($\beta_{Latitude:Marine}$=-0.005, $p$=0.007 and
$\beta_{Latitude:Terrestrial}$=-0.005, $p$=0.001). Scaling of mean vulnerability with
species richness showed the same pattern ($\beta_{Latitude}$=0.004, $p$\textless0.001;
$\beta_{Latitude:Marine}$=-0.005, $p$=0.007; and $\beta_{Latitude:Terrestrial}$=-0.005, $p$=0.002).
In contrast, scaling of mean generality with species richnesss increased with latitude 
for lake food webs ($\beta_{Latitude:Lake}$=0.006, $p$=0.002) but did not vary with latitude for
other ecosystem types ($\beta_{Latitude}$=-0.001, $p$=0.199).

>>>>

We compiled a list of 263 empirical food webs from
multiple sources (see Supplemental Information for web origins and selection
criteria). We recorded study site latitude from the original source where
possible or, where study sites were described but exact coordinates were not
given, obtained estimated coordinates using Google Earth \citep{GoogleEarth}.
We then divided the species in each web into basal resources (those species with
consumers but no prey), top predators (those species with prey but no predators),
and intermediate consumers (species with both predators and prey, including cannibalistic
species). For our future analyses, we considered only those webs with at least one basal
resource, one intermediate consumer, and one top predator. This reduced our dataset to
163 food webs.

@@

For relationships of $Z$, $G$, $V$, $B$, $I$, and $T$ to $S$, equation~\ref{LogLog} had a
lower AIC than the corresponding equation~\ref{Power}. This indicates that the
data support an assumption of multiplicative log-normal error better than an
assumption of additive normal error. That is, models where $\epsilon$ is
modelled as an exponent to a multiplicative term (that is, an additive term on
the logarithmic scale) provide a better description of the data than models
where $\epsilon$ is modelled as an additive term on the arithmetic scale
[[That's what this means... not sure if explaining it actually adds anything
though]] .  We therefore used logarithmic-form models when assessing the
effect of latitude on scaling relationships  with $S$.

Contrary to the expected latitudinal gradient, the best-fit version of
equation~\ref{Latfull} for $S$ included a signficant effect of latitude on $S$
in stream webs only ($\alpha_{Latitude:Stream}$=-1.69, $p$=0.007).  This
relationship was robust to the removal of three outliers (post-removal
$\alpha_{Latitude:Stream}$=-1.17, $p$=0.038). The best-fit versions of
equation~\ref{Latfull} for $Z$ and $V$ also included relatioships with
latitude in stream webs ($\alpha_{Latitude:Stream}$=-0.179, $p$=0.007 and
$\alpha_{Latitude:Stream}$=-0.179, $p$=0.007, respectively). However, after
the removal of three outlying stream webs with very high $Z$ and $V$ (two of
which also had unusually high $S$) these relationships were no longer
significant ($\alpha_{Latitude:Stream}$=-0-0.046, $p$=0.373 and
$\alpha_{Latitude:Stream}$=-0.046, $p$=0.373, respectively). Marine food webs
had lower $S$, $Z$, $G$, and $V$ than all other web types (post-removal
$\alpha_{Marine}$=-29.5, $p$\textless0.001, $\alpha_{Marine}$=-1.46,
$p$=0.035, $\alpha_{Marine}$=-1.74, $p$=0.0612, and $\alpha_{Marine}$=-1.46,
$p$=0.035, respectively) while stream food webs had higher $G$ than webs from
other ecosystem types (post-removal $\alpha_{Stream}$=3.51,
$p$\textless0.001).

As with $S$, $B$ increased slightly with latitude ($\alpha_{Latitude}$=0.001, $p$=0.139). Unlike with $S$, the scaling 
relationship was stronger in stream food webs ($\alpha_{Latitude:Stream}$=0.012, $p$\textless0.001). 
Scaling of $I$ with latitude did not vary with latitude or across
ecosystem types. 
As with $S$ and $B$, scaling of $T$ increased slightly with 
latitude ($\alpha_{Latitude}$=0.001, $p$=0.136). As with $S$,
this trend was reversed in stream food webs ($\alpha_{Latitude:Stream}$=-0.006, $p$=0.030) and was also reversed in 
lake food webs ($\alpha_{Latitude:Lake}$=-0.006, $p$=0.001).
All of the above trends were robust to the removal of outliers.

\subsection*{Effect of Latitude on Scaling with S, B, I, and T}

The effect of latitude on scaling relationships varied across ecosystem types.
Specialization in lake food webs decreased towards the poles [[LS, Gen, Vul
increased]] (Fig.~\ref{}), while in stream food webs $G$ increased towards the
poles but $Z$ and $V$ were unaffected.  These trends were robust to the
removal of outliers. [[Scaling of BIT with latitude?]]

[[Makes more sense to go property by property, do BIT with S].]

More specifically, the scaling of $V$ with $S$ was slightly stronger towards
the equator in estuarine, marine, stream, and terrestrial food webs
($\alpha_{Latitude}$=-0.001, $p$=0.267) but stronger towards the poles in
stream food webs ($\alpha_{Latitude:Lake}$=0.005, $p$=0.008; Fig.~\ref{}).
This scaling relationship was not consistent across different trophic levels.
Scaling of $V$ with the proportion of basal resources was  stronger towards
the poles in estuarine, lake, and stream food webs
($\alpha_{Latitude}$=-0.007, $p$=0.006),  stronger towards the equator in
terrestrial food webs ($\alpha_{Latitude:Terrestrial}$=0.013, $p$=0.002), and
nearly neutral in marine food webs ($\alpha_{Latitude:Marine}$=0.009,
$p$=0.047).  Scaling of $V$ with the proportion of intermediate consumers did
not vary across latitude for any ecosystem type.  Scaling was weaker in lake
and stream ecosystems ($\alpha_{Lake}$=-0.170, $p$=0.019 and
$\alpha_{Stream}$=-0.430, $p$\textless0.001, respectively) than in other
ecosystem types. Scaling of $V$ with the proportion of top predators generally
showed a similar pattern to scaling of $V$ with the proportion of basal
resources. Scaling was slightly stronger towards the equator for lake, marine,
and estuarine food webs ($\alpha_{Latitude}$=-0.001, $p$=0.52) but stronger
towards the poles for terrestrial and stream food webs
($\alpha_{Latitude:Terrestrial}$=0.006, $p$=0.067;
$\alpha_{Latitude:Stream}$=0.015, $p$\textless0.001).

The scaling of $G$ with $S$ folowed a somewhat similar pattern to the scaling
of $Z$ with $S$.  Scaling was slightly stronger towards the equator in
estuarine, marine, and terrestrial food webs ($\alpha_{Latitude}$=-0.001,
$p$=0.363) but stronger towards the poles in lake and stream food webs
($\alpha_{Latitude:Lake}$=0.005, $p$=0.002 and
$\alpha_{Latitude:Stream}$=0.007, $p$=0.002).  The scaling of $G$ with the
proportion of basal resources was stronger towards the poles in estuarine,
stream, and lake food webs ($\alpha_{Latitude}$=-0.009, $p$=0.002) but this
trend was reversed for terrestrial and marine webs
($\alpha_{Latitude:Marine}$=0.011, $p$=0.028;
$\alpha_{Latitude:Terrestrial}$=0.015, $p$=0.001). Similarly, the scaling of
$G$ with the proportion of intermediate consumers was stronger towards the
equator in [[The picture doesn't match the betas... maybe because of - scaling
with latitude and with ecosystem type?]] Scaling of $G$ with the proportion of
top predators did not vary across latitude. Scaling was strongest in stream
ecosystems ($\alpha_{Stream}$=-0.344, $p$\textless0.001) and weakest in marine
food webs ($\alpha_{Marine}$=0.170, $p$=0.008).

Scaling of $V$ with $S$ was slightly stronger towards the equator
($\alpha_{Latitude}$=-0.001, $p$=0.267; Fig.~\ref{}) except in lake food webs
where scaling was stronger towards the poles ($\alpha_{Latitude:Lake}$=0.005,
$p$=0.008). When scaling was broken up by trophic level, however, lake food
webs were not so exceptional. Scaling of $V$ with $B$ was stronger towards the
poles in estuarine, lake and stream food webs ($\alpha_{Latitude}$=-0.007,
$p$=0.006). This trend was reversed for marine and terrestrial food webs
($\alpha_{Latitude:Marine}$=0.009, $p$=0.047;
$\alpha_{Latitude:Terrestrial}$=0.013, $p$=0.002). Scaling of $V$ with $I$ was
not affected by latitude in any ecosystem type.  Scaling of $V$ with $T$ was
slightly stronger towards the equator in estuarine, marine, and lake food webs
($\alpha_{Latitude}$=-0.001, $p$=0.521) but stronger towards the equator in
stream and terrestrial food webs ($\alpha_{Latitude:Stream}$=0.015,
$p$\textless0.001; $\alpha_{Latitude:Terrestrial}$=0.006, $p$=0.067).
